Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-25 Methods-and-Results.Rmd
paragraph check

We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"]`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"]`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).

\paragraph{Core Need}

>>>>

We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"] %>% round(2) %>% format(nsmall=2)`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"] %>% round(2) %>% format(nsmall=2)`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance. This is unusual because this might indicate the the effect is very consistent across participants. However, this might also be the case due to a small number of participants, or other measurement issues.}. Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants, keeping in mind that the between-participant analyses in the aggregated form are based in a small sample size.

\paragraph{Core Need}t be explained by whether or not the interaction fulfilled the person's core situational need. This should, in turn, be due to a higher perceived interaction quality. We will this sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.

### 2021-10-25 Methods-and-Results.tex
paragraph check

We additionally used a multilevel regression to check whether having an
interaction with an outgroup member had a situational (i.e.,
contemporaneous) effect within the participants. We find that having an
outgroup interaction is indeed associated with significantly more
positive outgroup attitudes within the participants (\textit{b} = 2.48,
\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
\textit{95\%CI}{[}1.3644, 3.5884{]}), even after controlling for having
an interaction with a non-Dutch (which did not relate to outgroup
attitudes independently; For full results see Online Supplementary
Materials B).

@@

>>>>

We additionally used a multilevel regression to check whether having an
interaction with an outgroup member had a situational (i.e.,
contemporaneous) effect within the participants. We find that having an
outgroup interaction is indeed associated with significantly more
positive outgroup attitudes within the participants (\textit{b} = 2.48,
\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
interaction with a non-Dutch (which did not relate to outgroup attitudes
independently; For full results see Online Supplementary Materials
B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance. This is unusual because this might indicate the the effect is very consistent across participants. However, this might also be the case due to a small number of participants, or other measurement issues.}.
Thus, in our first data we find mixed results, where outgroup contacts
show a positive effect on outgroup attitudes in the moment but these
results do not translate into average differences between participants,
keeping in mind that the between-participant analyses in the aggregated
form are based in a small sample size.

@@

t be explained by whether or not the interaction fulfilled the person's
core situational need. This should, in turn, be due to a higher
perceived interaction quality. We will this sequentially test whether
the fulfillment of the core need during an interaction is (1) related to
more positive outgroup attitudes, (2) higher perceived interaction
quality, and (3) whether the variance explained by the core need is
assumed by the perceived interaction quality if considered jointly.
